Risk Perceptions for Wearable Devices

### 2015-04-15 tex-inputs/results-openended.tex
more small changes

This question was asked along with demographics questions (but before any IUIPC questions, which asked a lot of direct privacy-related questions, to avoid biasing the recipients). The participants were presented with a blank box to write in, with no character limit to their open-ended responses.

>>>>

This question was asked with demographics questions, but before any IUIPC questions (which asked a lot of direct privacy-related questions, to avoid biasing the recipients). The participants were presented with a blank box to write in, with no character limit to their open-ended responses.

### 2015-04-15 tex-inputs/results-regression.tex
more small changes

\subsubsection{Regression Models} 
\label{sec:regression}
In order to examine the relative effect of each factor on participants' VURs, we constructed several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes). We performed binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).

@@

We created several models using two independent variables as predictors: data and recipient. Because the device (i.e., whether they were using the Cubetastic3000 or a smartphone) was only varied for the 5 smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these five  from our models, which resulted in a total of 72 types of data shared with 4 possible recipients. We also used collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score. For each model, we performed Wald's test to examine the model effects attributable to each of these parameters. The only covariates that had an observable effect on our models were gender and participants' IUIPC scores, which also exhibited an interaction effect with each other. Thus, we opted to remove the other covariates from our analysis. Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection that also accounts for complexity (lower relative values indicate better fit). As can be seen, the data type was the strongest predictor of VUR. The coefficients for the model with the best fit can be seen in Appendix \ref{sec:regression-apx}.

@@

With regard to data types, the most concerning type of data was video (78.0\%), which was ranked similarly to photos (76.2\%). Next were audio (66.8\%) and demographic data (65.4\%), followed by behavioral (53.1\%) and biometric (46.3\%) data. We suspect that demographic data was more concerning because it included information such as a Social Security Number, bank account information, and other financial information. We chose to categorize them as such as they are non-biological descriptors of the user. We were very surprised that biometric information was seen as relatively benign compared to the other broad categories of data. One hypothesis is that since most home users do not use biometric authentication, they may have an inaccurate understanding of the types of systems that might be at risk if biometric data are stolen and abused.

@@

Using these two new variables as additional independent variables (and removing the previous data type variable), we created a second set of models. Because these risk categories and mediums are less likely to change over time, models that take these into account are likely to be more useful and less likely to be overfit. What these models show us is that both risk and medium are relatively strong predictors by themselves, and have an even stronger interaction effect. When the data recipient and covariates are added to the model, the resulting goodness-of-fit is not much worse than that of the model using the actual data type. The full model can be found in Appendix \ref{sec:regression-apx2}.

>>>>

\subsubsection{Regression Models} 
\label{sec:regression}
In order to examine the relative effect of each factor on participants' VURs, we construct several statistical models to predict whether a participant would be ``very upset'' with a given scenario based on the data type, data recipient, and their demographic factors (i.e., age, education, gender, and privacy attitudes). We perform binary logistic regressions using generalized estimating equations, which account for our repeated measures experimental design (i.e., each participant contributed multiple data points).

@@

We create several models using two independent variables as predictors: data and recipient. Because the device (i.e., whether they were using the Cubetastic3000 or a smartphone) is only varied for the five smartphone misbehaviors listed in Section \ref{sec:smartphones}, we removed these five  from our models, which resulted in a total of 72 types of data shared with 4 possible recipients. We also used collected demographic factors as covariates: age, gender, education, wearable device ownership (yes/no), and mean IUIPC score. For each model, we performed Wald's test to examine the model effects attributable to each of these parameters. The only covariates that had an observable effect on our models were gender and participants' IUIPC scores, which also exhibited an interaction effect with each other. Thus, we opted to remove the other covariates from our analysis. Table \ref{regression} shows the various models that we examined and the Quasi-Akaike Information Criterion (QIC), which is a goodness-of-fit metric for model selection that also accounts for complexity (lower relative values indicate better fit). As can be seen, the data type was the strongest predictor of VUR. The coefficients for the model with the best fit can be seen in Appendix \ref{sec:regression-apx}.

@@

With regard to data types, the most concerning type of data is video (78.0\%), which was ranked similarly to photos (76.2\%). Next are audio (66.8\%) and demographic data (65.4\%), followed by behavioral (53.1\%) and biometric (46.3\%) data. We suspect that demographic data was more concerning because it included information such as a Social Security Number, bank account information, and other financial information. We chose to categorize them as such as they are non-biological descriptors of the user. We were very surprised that biometric information was seen as relatively benign compared to the other broad categories of data. One hypothesis is that since most home users do not use biometric authentication, they may have an inaccurate understanding of the types of systems that might be at risk if biometric data is stolen and abused.

@@

Using these two new variables as additional independent variables (and removing the previous data type variable), we created a second set of models. Because these risk categories and mediums are less likely to change over time, models that take these into account are likely to be more useful and less likely to be overfit. What these models show us is that both risk and medium are relatively strong predictors by themselves, and have an even stronger interaction effect. When the data recipient and covariates are added to the model, the resulting goodness-of-fit is not much worse than that of the model using the actual data type. %The full model can be found in Appendix \ref{sec:regression-apx2}.
